---
title: "Landscape Phase 1 Data Collection"
author: "Meng Liu"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---
# Load libraries
```{r}
pacman::p_load(bibliometrix,tidyverse)
```

# Note on the search
Search string:
TI = (“open science” OR “open research” OR “open scholarship”) OR AK = (“open science” OR “open research” OR “open scholarship”) OR KP = (“open science” OR “open research” OR “open scholarship”)

Editions = A&HCI , BKCI-SSH , BKCI-S , CCR-EXPANDED , ESCI , IC , CPCI-SSH , CPCI-S , SCI-EXPANDED , SSCI 

Screenshot of search was saved as "Search screenshot 20220626.png".

Link to query:
https://www.webofscience.com/wos/woscc/summary/02f9842c-7756-41a7-9229-0798510200fb-401bcfdc/relevance/1

The search returned 2,355 hits.

All fields were then exported as BibTex (in five batches as the maximum export for each batch is 500). 

# Load raw data 
```{r}

files <- c("raw data/savedrecs(1).bib",
           "raw data/savedrecs(2).bib",
           "raw data/savedrecs(3).bib",
           "raw data/savedrecs(4).bib",
           "raw data/savedrecs(5).bib")

raw_data <- convert2df(files, dbsource = "wos", format = "bibtex")
```


AU Authors
TI Document Title
SO Publication Name (or Source)
JI ISO Source Abbreviation
DT Document Type
DE Authors’ Keywords
ID Keywords associated by SCOPUS or WoS database
AB Abstract
C1 Author Address
RP Reprint Address
CR Cited References
TC Times Cited
PY Year
SC Subject Category
UT Unique Article Identifier
DB Database


# Preprocessing
```{r}
# preprocess data 
data <- raw_data %>% 
    as_tibble() %>% 
    # assign unique ID
    mutate(unique_id = row_number()) %>% 
    # rename col with descriptive labels
    rename(title = TI,
           author_keywords = DE,
           abstract = AB,
           keywords_plus = ID,
           doi = DI)
```

# Subset pilot sample for screening 
```{r}
set.seed(123)

pilot_screening <- data %>%
    select(unique_id, title, author_keywords, abstract, keywords_plus, doi) %>% 
    mutate_all(.,str_to_lower) %>% 
    sample_n(size = 100) 
    
rio::export(pilot_screening,"pilot_screening.csv")

```

# Subset pilot sample for tagging 
```{r}
set.seed(123)

data %>%
   summarise(sum(is.na(author_keywords)))

```

At the moment there are 594 without author keywords which is on the large side (especially for double coding). We will wait after screening pilot to see if the number for this is reduced. 


